Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-07-16 ATVA 2025/Final_version/proofsb.tex
update the final version

Hybird MILP first call $\alpha,\beta$-Crown with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-Crown. We are using two settings of TO, for smaller DNNs we use TO$=10s$, and for the two larger ones, we use TO$=30s$.

Partial MILP uses 20 CPU-threads, while $\alpha,\beta$-Crown uses massively parallel ($>$4096 threads) GPU,

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c||}
		\hline \hline
		Network & TO for $\alpha,\beta$-Crown  & Minimum number of Open neurons  \\ 		  
		\hline
		MNIST $5 \times 100$ & 10s  & 48,21,11,6,14  \\ \hline
		MNIST $5 \times 200$ & 10s & 48,21,11,6,14  \\ \hline
		MNIST $8 \times 100$ & 10s  & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $8 \times 200$ & 10s & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $6 \times 500$ & 30s & 48,21,11,6,3,14 \\ \hline
		CIFAR CNN-B-adv & 30s & 200, 0, 45 \\ \hline \hline
	\end{tabular}
	\caption{Settings of Hybrid MILP for the different {\em hard} instances}
	\label{table20}
	\end{table}

@@

Notice that a different balance between accuracy and runtime could be set. For instance, we set up the numbers of open neurons to have similar runtime as Refined $\beta$-Crown for the first 4 DNNs ($50s-100s$). We could easily target better accuracy (e.g. for $8 \times 100$ with a relatively high $15\%$ undecided images) by increasing the number of open neurons, with a trade-off on runtime (current runtime is at $61s$).
By comparison, the sweet spot for $\alpha,\beta$-Crown seems to be around TO$=30s$, enlarging the time-out having very little impact on accuracy but large impact on runtime
(Table \ref{table_beta}).

\subsection*{Setting for $\alpha,\beta$-Crown}

The networks were already tested by $\alpha,\beta$-Crown \cite{crown}. We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github}, 
except for time-out which we explicitly mention:
e.g. for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20"; and
for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".

%We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to. From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-Crown on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP. The conclusion are thus unchanged.

@@

In the following, we provide results comparing $\alpha,\beta$-Crown to other verifiers, to justify our use of $\alpha,\beta$-Crown as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.

\subsection*{Comparison $\alpha,\beta$-Crown vs PRIMA}

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c|c||c||}
		\hline \hline
		Network & $\alpha,\beta$-Crown & Refined $\beta$-Crown & PRIMA \\ 		  
		\hline
		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
		CIFAR CNN-B-adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves. N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-Crown cannot be run on these DNNs.}
	\label{table9}
	\begin{tablenotes}
		\footnotesize
		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
	\end{tablenotes}
	\end{table}

	PRIMA \cite{prima} is a major verifier in the ERAN toolkit. In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-Crown, mainly from \cite{crown}. The setting is mainly similar from ours, but numbers are not perfectly comparable as the images tested are not  exactly the same (1000 first or 200 first images for CNN-B-Adv), vs 100 first in Tables \ref{table_hybrid}, \ref{table_beta}. Also, time-out settings and hardware are slightly different. The overall picture is anyway the same.

Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-Crown. However, it is slower and less accurate than Refined $\beta$-Crown.
On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-Crown, while the runtime is $>5$ times larger.
Hence, Hybrid MILP is more accurate than PRIMA with similar runtime or faster.

@@

\subsection*{Comparison $\alpha,\beta$-Crown vs MN-BaB}

MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-Crown. Results in \cite{ferrari2022complete}
are close to those of $\alpha,\beta$-Crown. However, none of the {\em hard} networks from \cite{crown} that we consider have been tested. We thus tested three representative {\em hard} DNNs (first 100 images) to understand how MN-BaB fairs on such hard instances, and report the numbers in Table \ref{table10}. Results are directly comparable with Table \ref{table_hybrid}.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c|c||c|c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & MN-BaB & MN-BaB \\ 
		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
		\hline
		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
		CIFAR CNN-B-adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown, and MN-BaB}
	\label{table10}
\end{table}

Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-Crown. Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.

	\subsection*{Comparison $\alpha,\beta$-Crown vs NNenum}

NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-Crown. The experiments section in \cite{nnenum} does not report
the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
$6 \times 500$ and CIFAR CNN-B-adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-Crown, on both 
MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-Crown, but far from the accuracy Hybrid MILP.
On CIFAR CNN-B-adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c||c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & NNenum & Hybrid\\ 
		 Network & TO=2000s &  TO=2000s & MILP\\ 
		\hline
		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
		CIFAR CNN-B-adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-Crown and NNenum with 2000s time-out, and Hybrid MILP}.
	\label{table11}
\end{table}

@@

\begin{table}[h!]
	\centering
	\begin{tabular}{||l|c|c||}
		\hline
		Network & average time & maximum time \\ \hline
		MNIST 5$\times$100 & 0.41s & 1.87 \\
		$\epsilon = 0.026$ &  & \\  \hline
		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 8$\times$100 & 0.39s & 1.41s \\
		$\epsilon = 0.026$ & &  \\  \hline
		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 6$\times$500 & &   \\ 
		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
		CIFAR CNN-B-adv &  & \\
		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
	\end{tabular}
	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
	\label{table112}
\end{table}

>>>>

Hybird MILP first call $\alpha,\beta$-CROWN with short time-out (TO), then call partial MILP on those inputs which was neither certified nor falsified by this run of $\alpha,\beta$-CROWN. We are using two settings of TO, for smaller DNNs we use TO$=10s$, and for the two larger ones, we use TO$=30s$.

Partial MILP uses 20 CPU-threads, while $\alpha,\beta$-CROWN uses massively parallel ($>$4096 threads) GPU,

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c||}
		\hline \hline
		Network & TO for $\alpha,\beta$-CROWN  & Minimum number of Open neurons  \\ 		  
		\hline
		MNIST $5 \times 100$ & 10s  & 48,21,11,6,14  \\ \hline
		MNIST $5 \times 200$ & 10s & 48,21,11,6,14  \\ \hline
		MNIST $8 \times 100$ & 10s  & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $8 \times 200$ & 10s & 48,21,11,6,3,2,1,14  \\ \hline
		MNIST $6 \times 500$ & 30s & 48,21,11,6,3,14 \\ \hline
		CIFAR CNN-B-Adv & 30s & 200, 0, 45 \\ \hline \hline
	\end{tabular}
	\caption{Settings of Hybrid MILP for the different {\em hard} instances}
	\label{table20}
	\end{table}

@@

Notice that a different balance between accuracy and runtime could be set. For instance, we set up the numbers of open neurons to have similar runtime as Refined $\beta$-CROWN for the first 4 DNNs ($50s-100s$). We could easily target better accuracy (e.g. for $8 \times 100$ with a relatively high $15\%$ undecided images) by increasing the number of open neurons, with a trade-off on runtime (current runtime is at $61s$).
By comparison, the sweet spot for $\alpha,\beta$-CROWN seems to be around TO$=30s$, enlarging the time-out having very little impact on accuracy but large impact on runtime
(Table \ref{table_beta}).

\subsection*{Setting for $\alpha,\beta$-CROWN}

The networks were already tested by $\alpha,\beta$-CROWN \cite{crown}. We thus simply reused the parameter files from \href{https://github.com/Verified-Intelligence/alpha-beta-CROWN/blob/main/complete_verifier/exp_configs/beta_crown/}{their Github}, 
except for time-out which we explicitly mention:
e.g. for CNN-B-Adv: "solver: batch size: 512 beta-crown: iteration: 20"; and
for MNIST 5x100: "solver: batch size: 1024 beta-crown: iteration: 20".

%We did not experiment with cutting planes (GCP-CROWN \cite{cutting}), as it needs an additional package, namely IBM CPLEX solver, we do not have access to. From \cite{cutting}, the number of undecided inputs of GCP-CROWN is $\leq 2\%$ better than $\alpha,\beta$-CROWN on the DNNs we experimented with, far from the $10-40\%$ improvement seen from Hybrid MILP. The conclusion are thus unchanged.

@@

In the following, we provide results comparing $\alpha,\beta$-CROWN to other verifiers, to justify our use of $\alpha,\beta$-CROWN as state of the art for efficient verifiers as main source of comparison to Hybrid MILP for hard DNN instance.

\subsection*{Comparison $\alpha,\beta$-CROWN vs PRIMA}

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c|c||c||}
		\hline \hline
		Network & $\alpha,\beta$-CROWN & Refined $\beta$-CROWN & PRIMA \\ 		  
		\hline
		MNIST $5 \times 100$ & N/A  & 14.3\% (102s) & 33.2\% (159s)\\ \hline
		MNIST $5 \times 200$ & N/A & 13.7\% (86s) & 21.1\% (224s) \\ \hline
		MNIST $8 \times 100$ & N/A  & 20.0\% (103s) & 39.2\% (301s)   \\ \hline
		MNIST $8 \times 200$ & N/A & 17.6\% (95s) & 28.7\% (395s)  \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & $-$ & 64\% (117s) \\ \hline
		CIFAR CNN-B-Adv & 18.5\% (32s) & $-$ & 27\% (344s)\\ \hline \hline
		CIFAR ResNet & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN, Refined $\beta$-CROWN, and PRIMA, as reported in \cite{crown}, except for $6 \times 500$ that we run ourselves. N/A means that \cite{crown} did not report the numbers, while $-$ means that Refined $\beta$-CROWN cannot be run on these DNNs.}
	\label{table9}
	\begin{tablenotes}
		\footnotesize
		\item Most data is directly from \cite{crown}. N/A means no data either in \cite{crown} or by our running.
		\item  $^*$ The data in this row is from our own running on first 100 images of the MNIST dataset.
		\item  $^{**}$ The data is from \cite{crown} on first 200 images of the CIFAR10 dataset.
	\end{tablenotes}
	\end{table}

	PRIMA \cite{prima} is a major verifier in the ERAN toolkit. In Table \ref{table9}, we report the comparison between PRIMA and $\alpha,\beta$-CROWN, mainly from \cite{crown}. The setting is mainly similar from ours, but numbers are not perfectly comparable as the images tested are not  exactly the same (1000 first or 200 first images for CNN-B-Adv), vs 100 first in Tables \ref{table_hybrid}, \ref{table_beta}. Also, time-out settings and hardware are slightly different. The overall picture is anyway the same.

Analysis: On the 4 smallest MNIST networks, PRIMA uses a refined path comparable with Refined $\beta$-CROWN. However, it is slower and less accurate than Refined $\beta$-CROWN.
On larger {\em hard} networks, PRIMA has also more undecided images than $\alpha,\beta$-CROWN, while the runtime is $>5$ times larger.
Hence, Hybrid MILP is more accurate than PRIMA with similar runtime or faster.

@@

\subsection*{Comparison $\alpha,\beta$-CROWN vs MN-BaB}

MN-BaB \cite{ferrari2022complete} is an improvement built over PRIMA, using a similar Branch and Bound technique as used in $\alpha,\beta$-CROWN. Results in \cite{ferrari2022complete}
are close to those of $\alpha,\beta$-CROWN. However, none of the {\em hard} networks from \cite{crown} that we consider have been tested. We thus tested three representative {\em hard} DNNs (first 100 images) to understand how MN-BaB fairs on such hard instances, and report the numbers in Table \ref{table10}. Results are directly comparable with Table \ref{table_hybrid}.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c|c||c|c||}
		\hline \hline
		 & $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN & MN-BaB & MN-BaB \\ 
		 Network & TO=30s & TO=2000s &  TO=30s & TO=2000s \\ 
		\hline
		MNIST $5 \times 100$ & 55\% (19s) & 50\%(1026s) & 60\% (19s) & 50\% (1027s) \\ \hline
		MNIST $6 \times 500$ & 51\% (16s) & 50\% (1002s) & 58\% (18s) & 55\% (1036s) \\ \hline
		CIFAR CNN-B-Adv & 22\% (8.7s) & 20\% (373s) & 43\% (14s) & 24\% (576s) \\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN, and MN-BaB}
	\label{table10}
\end{table}

Analysis: results reveal that MN-BaB is slightly slower and slightly less accurate than $\alpha,\beta$-CROWN. Notice the specially high number of undecided images for CNN-B-Adv with TO=30s, probably meaning that 30s is too small for MN-BaB on this large DNN.
Hence, Hybrid MILP is more accurate than MN-BaB with similar runtime or faster.

	\subsection*{Comparison $\alpha,\beta$-CROWN vs NNenum}

NNenum \cite{nnenum} is a complete verifier with good performance according to VNNcomp.
It was the only complete verifier tested in Table \ref{table_complete} to verify more images than $\alpha,\beta$-CROWN. The experiments section in \cite{nnenum} does not report
the {\em hard} DNNs we are considering. We tried to experiment it on the same MNIST 
$6 \times 500$ and CIFAR CNN-B-Adv as we did in Table \ref{table10} for MN-BaB. Unfortunately, on $6 \times 500$, buffer overflow were reported.
We report in Table \ref{table11} experiments with the same 2000s Time-out (it was $10 000s$ in Table \ref{table_complete})  for a fair comparison with $\alpha,\beta$-CROWN, on both 
MNIST $5 \times 100$ and CIFAR CNN-B-Adv. 
On MNIST $5 \times 100$, NNenum is slightly more accurate than $\alpha,\beta$-CROWN, but far from the accuracy Hybrid MILP.
On CIFAR CNN-B-Adv, NNenum was much less accurate than $\alpha,\beta$-CROWN, and thus of Hybrid MILP. In both test, the runtime of NNenum was also much longer than for Hybrid MILP.

\begin{table}[h!]
	\centering
	\begin{tabular}{||l||c||c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-CROWN & NNenum & Hybrid\\ 
		 Network & TO=2000s &  TO=2000s & MILP\\ 
		\hline
		MNIST $5 \times 100$ & 50\%(1026s) & 44\% (1046s) & \bf 13\% (46s)\\ \hline
		CIFAR CNN-B-Adv & 20\% (373s) & 40\% (1020s) & \bf 11\% (417s)\\ \hline 
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), as computed by $\alpha,\beta$-CROWN and NNenum with 2000s time-out, and Hybrid MILP}.
	\label{table11}
\end{table}

@@

\begin{table}[h!]
	\centering
	\begin{tabular}{||l|c|c||}
		\hline
		Network & average time & maximum time \\ \hline
		MNIST 5$\times$100 & 0.41s & 1.87 \\
		$\epsilon = 0.026$ &  & \\  \hline
		MNIST 5$\times$200 &  0.75s & 5.31s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 8$\times$100 & 0.39s & 1.41s \\
		$\epsilon = 0.026$ & &  \\  \hline
		MNIST 8$\times$200 & 0.49s & 1.63s \\ 
		$\epsilon = 0.015$ & & \\  \hline
		MNIST 6$\times$500 & &   \\ 
		$\epsilon = 0.035$ & 1.4s & 3.5s \\ 
		$\epsilon = 0.1$ & 44.6s & 310s \\  \hline 
		CIFAR CNN-B-Adv &  & \\
		$\epsilon = 2/255$& 1s & 609s \\ \hline \hline
	\end{tabular}
	\caption{average and maximum time per $\MILP_X$ calls for image 3 (MNIST) and image 76 (CIFAR10).}
	\label{table112}
\end{table}

### 2025-07-16 ATVA 2025/Final_version/relatedwork.tex
update the final version

We compare Hybrid MILP with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art. It scales while preserving good accuracy, through targeting a limited number of binary variables, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate). MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding. In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more \textcolor{red}{binary variables} (thus runtime) to reach the same accuracy.
% as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

>>>>

We compare Hybrid MILP with major verification tools for DNNs to clarify our methodology and its distinction from the existing state-of-the-art. It scales while preserving good accuracy, through targeting a limited number of binary variables, stricking a good balance between exact encoding of a DNN using MILP~\cite{MILP} (too slow) and LP relaxation (too inaccurate). MIPplanet~\cite{MIPplanet} opts for a different selection of binary variables, and execute one large MILP encoding instead of Hybrid MILP's many small encodings, which significantly reduce the number of binary variables necessary for each encoding. In \cite{DivideAndSlide}, small encodings are also considered, however with a straightforward choice of binary nodes based on the weight of outgoing edges, which need much more {binary variables} (thus runtime) to reach the same accuracy.
% as our utility function (see Table \ref{tab:example1}), and restrict integer variables to the previous layer, which limits the accuracy reachable.

### 2025-07-16 ATVA 2025/Final_version/valabstraction.tex
update the final version

Consider the simpler abstraction, termed ``Box abstraction", recalled e.g. in \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently. This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth. 
For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$. This implies that $x_3,x_4 \in [-2,2]$. After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to \textcolor{red}{$[1.5,3.5]$} , leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$. 
The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$. However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons. For example, it is impossible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $x_3=2$ and $x_4=2$, which is not possible at the same time as 
$x_3=2$ implies $x_1=x_2=1$ and $x_4=2$ implies $x_2=-1$ (and $x_1=1$), a contradiction.

@@

For all $x \in [\LB,\UB] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}. The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$. This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds. However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous \textcolor{red}{binary variables} and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.

@@

To reduce the runtime, we will limit the size of subset $X$. This a priori hurts accuracy. To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of \textcolor{red}{each layer} iteratively, that are used when computing values of the next layer.
So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.

@@

We provide the pseudo code for pMILP$_K$ in Algorithm \ref{algo1}.
pMILP$_K$ has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ \textcolor{red}{binary variables} and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound. Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$. This worst-case complexity compares favorably when $K<<N$ with the worst-case complexity of BaB which would be $O(out \times 2^N)$, where $out$ is the number of output neurons. Of course, actual complexity is always much better than the worst case, thanks to different heuristics, such as pruning, which is what happens for easy instances, for which the linear cost $N$ in pMILP (which cannot be avoided) is actually the limiting factor. Only experimental results can tell whether the accuracy lost using reduced variables in pMILP can be a good trade off vs efficiency, both depending on the number $K$ chosen.
%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
%pMILP uses 20 threads.

>>>>

Consider the simpler abstraction, termed ``Box abstraction", recalled e.g. in \cite{deeppoly}: it inductively computes the bounds for each neuron in the subsequent layer independently. This is achieved by considering the weighted sum of the bounds from the previous layer, followed by clipping the lower bound at $\max(0,$ lower bound$)$ to represent the ReLU function, and so forth. 
For all $i \geq 3$, define $x_i=\val_{\vx}(n_i)$, where $\vx=(x_1,x_2)$.
Taking the DNN example from Fig \ref{fig1}, assume $x_1,x_2 \in [-1,1]$. This implies that $x_3,x_4 \in [-2,2]$. After applying the ReLU function, $\hat{x}_3,\hat{x}_4$ are constrained to {$[1.5,3.5]$} , leading to $x_5 \in [0,6]$ and $x_6 \in [0,2]$. 
The bounds for $n_1, \ldots, n_4$ are exact, meaning for every $\alpha$ within the range, an input $\vy$ can be found such that $\val_{\vy}(n_i)=\alpha$. However, this precision is lost from the next layer (beginning with $n_5, n_6$) due to potential dependencies among preceding neurons. For example, it is impossible for $x_5=\Val_{\vx}(n_5)$ to reach $6$, as it would necessitate both $x_3=2$ and $x_4=2$, which is not possible at the same time as 
$x_3=2$ implies $x_1=x_2=1$ and $x_4=2$ implies $x_2=-1$ (and $x_1=1$), a contradiction.

@@

For all $x \in [\LB,\UB] \setminus 0$, there exists a unique solution $(a,\hat{x})$ that meets these constraints, with $\hat{x}=\ReLU(x)$ \cite{MILP}. The value of $a$ is 0 if $x < 0$, and 1 if $x>0$, and can be either if $x=0$. This encoding approach can be applied to every (unstable) ReLU node, and optimizing its value can help getting more accurate bounds. However, for networks with hundreds of {\em unstable} nodes, the resulting MILP formulation will contain numerous {binary variables} and generally bounds obtained will not be accurate, even using powerful commercial solvers such as Gurobi.

@@

To reduce the runtime, we will limit the size of subset $X$. This a priori hurts accuracy. To recover some of this accuracy, we use an iterative approach similar to the box abstraction or DeepPoly \cite{deeppoly}, computing lower and upper bounds $\LB,\UB$ for neurons $n$ of {each layer} iteratively, that are used when computing values of the next layer.
So we trade-off the NP-complexity in $|X|$ with a linear complexity in the number of neurons. Notice that all the neurons of a layer can be treated in parallel.

@@

We provide the pseudo code for pMILP$_K$ in Algorithm \ref{algo1}.
pMILP$_K$ has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ {binary variables} and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound. Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$. This worst-case complexity compares favorably when $K<<N$ with the worst-case complexity of BaB which would be $O(out \times 2^N)$, where $out$ is the number of output neurons. Of course, actual complexity is always much better than the worst case, thanks to different heuristics, such as pruning, which is what happens for easy instances, for which the linear cost $N$ in pMILP (which cannot be avoided) is actually the limiting factor. Only experimental results can tell whether the accuracy lost using reduced variables in pMILP can be a good trade off vs efficiency, both depending on the number $K$ chosen.
%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
%pMILP uses 20 threads.
